Concise Linkable Ring Signatures and Forgery Against Adversarial Keys

### 2020-03-30 paper/iacr.tex
Updated paper

\documentclass{article}
\usepackage[top=1.0in,bottom=1.0in,left=1.0in,right=1.0in]{geometry}
\usepackage{amsmath,amssymb,amsthm,amsfonts}
\usepackage[utf8]{inputenc}
\usepackage{hyperref}
\usepackage{graphicx}

\title{Triptych: logarithmic-sized linkable ring signatures with applications}
\author{Sarang Noether and Brandon Goodell \\ Monero Research Lab \\ \texttt{\{sarang,surae\}.noether@protonmail.com}}
\date{\today}

\newcommand{\G}{\mathbb{G}}
\newcommand{\F}{\mathbb{F}}
\newcommand{\com}{\operatorname{Com}}
\newcommand{\hs}{\mathcal{H}}
\newcommand{\hp}{\mathbb{H}}

\newcommand{\A}{\mathcal{A}}

\newcommand{\sumi}{\sum_{i=0}^{n-1}}
\newcommand{\sumj}{\sum_{j=0}^{m-1}}
\newcommand{\sumk}{\sum_{k=0}^{N-1}}

\newtheorem{theorem}{Theorem}
\theoremstyle{definition}
\newtheorem{definition}{Definition}

\begin{document}

\maketitle

\begin{abstract}
Ring signatures are a common construction used to provide signer ambiguity among a non-interactive set of public keys specified at the time of signing.
Unlike early approaches where signature size is linear in the size of the signer anonymity set, current optimal solutions either require centralized trusted setups or produce signatures logarithmic in size.
However, few also provide linkability, a property used to determine whether the signer of a message has signed any previous message, possibly with restrictions on the anonymity set choice.
Here we introduce Triptych, a family of linkable ring signatures without trusted setup that is based on generalizations of zero-knowledge proofs of knowledge of commitment openings to zero.
We demonstrate applications of Triptych in signer-ambiguous transaction protocols by extending the construction to openings of parallel commitments in independent anonymity sets.
Signatures are logarithmic in the anonymity set size and, while verification complexity is linear, collections of proofs can be efficiently verified in batches.
We show that for anonymity set sizes practical for use in distributed protocols, Triptych offers competitive performance with a straightforward construction.
\end{abstract}

\section{Introduction}
First introduced in \cite{rivest} with respect to RSA groups, ring signatures permit the signing of messages using public key sets not fixed in advance, without the need of a trusted group manager.
Earlier constructions lacked such flexibility, requiring either centralized key setup or the establishment of fixed signing sets.
Later work \cite{bender} established more robust security models for unforgeability and anonymity, capturing realistic threat models where an adversary is permitted to corrupt keys, convince honest signers to include malicious anonymity set members, or obtain signatures in advance.

Since a ring signature has an anonymity set of public keys, one of which is the true signer, the detection of signing by the same key requires an additional property, linkability.
A linkable ring signature \cite{lsag} enables verifiers to determine whether the (unknown) signer of a message has signed other messages.
Such a construction was proposed for election applications, where it is necessary to ensure that votes are anonymous, but voters are permitted to vote only once on a particular issue.
The construction in \cite{lsag}, with a hash-trapdoor structure similar to that of \cite{schnorr}, is of particular interest due to potential flexibility in linking; while its linking is limited to signer-selected but unchanging signer anonymity sets, it permits linking on a per-issue basis.
Additional recent work in \cite{backes} introduces the property of linkable anonymity, using sets of signatures and establishing restrictions on key corruption.
Other related interesting properties like traceability \cite{fs,f} imply stronger capabilities, where an attempt to sign two messages with the same key permits verifiers to identify the signer.

Linkable ring signatures have seen particular applications in signer-ambiguous transaction protocols.
In such an application, transactions are authorized by a ring signature whose signing anonymity set consists of previously-generated transaction outputs.
A signature demonstrates that the signer controls the private key of one such output without revealing which is the signer, and linkability is used to assure verifiers that output has not been used in another signature (signifying a double-spend attempt).

A practical consideration for the use of linkable ring signatures in transaction protocols is how signature size and verification time scale with the size of the anonymity set.
In common applied constructions like \cite{mlsag,clsag}, signature size and verification time scale linearly with the size of the signing ambiguity set; since such signatures are typically included in a public distributed data structure like a blockchain, there is a balance between the size of the anonymity set and the requirements for storage and verification.
Recent protocol work in this area mitigates the size restriction.
For example, in \cite{rct3}, the authors introduce a confidential transaction protocol based on a proving system whose size scales logarithmically with the anonymity set size, and which includes a method for demonstrating amount balance; amount commitment range proving is offloaded to other constructions like \cite{bulletproofs}.
In \cite{omniring}, the authors use a more general proving technique to accomplish a similar goal; however, the protocol offers further size benefits by integrating commitment range proofs into the proof structure directly, taking advantage of the logarithmic proof size.

Other signer-ambiguous transaction protocols not based on linkable ring signatures offer more competitive performance.
For example, protocols like \cite{zcash} produce maximal theoretical signer ambiguity through the use of zero-knowledge Merkle proofs (among others) that offer extremely small proofs with low verification time, but at the cost of a trusted structured setup process that arises from the underlying proving system \cite{groth16}.
Like this work, \cite{lelantus} is a transaction protocol also based on \cite{groth}; however, it is intended to operate on commitments similar to those used in \cite{zerocoin} but with the inclusion of amounts, and has limitations on addressing and sender tracing.

\subsection{Our contribution}
We produce two instantiations of a linkable ring signature, which we call Triptych.
The constructions are a linkable generalization of Groth's one-of-many commitment-to-zero proving system \cite{groth}, with optimizations from Bootle \cite{bootle} applied for improvements to proof size and verification complexity.
In one version of Triptych, the prover shows that it knows the opening of a commitment to zero within a commitment list, and also that it has constructed a linking tag using the same opening, enabling linkability.
We then modify Groth's ring signature definitions to include linkability and a related property, non-frameability.

In the second version of Triptych, we further generalize to include a parallel list of commitments.
Here, the prover proceeds as before to show its knowledge of an opening to a commitment in one list, as well as the construction of the linking tag.
However, the proof also shows that the prover knows an opening of a commitment at the same position in the second commitment list.
This construction has immediate application; in some signer-ambiguous confidential transaction protocols, transaction inputs are commitments to zero, for which the signer shows it knows the opening.
Each commitment comes equipped with another commitment to the amount of the input; by offsetting these commitments homomorphically and carefully choosing commitment randomness, the prover can show that a particular transaction balances.

We show that Triptych produces signatures with competitive performance to other modern linkable ring signatures for limited anonymity set sizes.
We note that similar constructions also require linear verification time, meaning that the size of anonymity set used in practice is likely to be limited for performance reasons.

\section{Preliminaries}
\subsection{Public parameters}
Let $\G$ be a cyclic group in which the discrete logarithm problem is hard, and let $\F$ be the scalar field of $\G$.
Let $\hs: \{0,1\}^* \to \F$ be a cryptographic hash function.
Let $G$ and $H$ be generators of $\G$ with unknown discrete logarithm relationship.
Let $N = n^m$ be a size parameter, where $n > 1$ and $m > 1$.
Let $\{G_{j,i}\}_{j,i=0}^{m-1,n-1}$ be a set of generators of $\G$ with unknown discrete logarithm relationship to each other, to $G$, and to $H$.
Let $U$ be a generator of $\G$.
Note that all generators may be produced using public randomness; for example, the use of a suitable hash function with domain separation may be appropriate.
All such public parameters are assumed to comprise a global reference string known to all players; in particular, we exclude them from algorithm definitions and Fiat-Shamir transcript hashes for readability.

\subsection{Pedersen commitment}
Let $\com$ be a homomorphic commitment scheme that is perfectly hiding and computationally binding.
In this work, we assume use of the Pedersen commitment scheme: for $x,r \in \F$, define $\com(x,r) \equiv xG + rH$ to be the commitment of the value $x$ with randomness $r$.
This can be trivially extended to support matrix values; for $\{x_{j,i}\},r \in \F$, define $\com(x,r) \equiv rH + \sum_{j,i} x_{j,i}G_{j,i}$.
Note in particular that Pedersen matrix commitments are similarly homomorphic.

\subsection{Other notation}
For integers or field elements $i,j$, the Kronecker delta function $\delta(i,j)$ evaluates to $1$ if $i=j$ and $0$ otherwise, where the output is taken to be in the appropriate set.

We sometimes use index subscript notation of the form $i_j$ to indicate the $j$ digit of $i$, where such a decomposition of $i$ is taken base $n$ with padded length $m$:
$$\sum_{j=0}^m i_j n^j = i$$
This notation will be specified explicitly where confusion may occur.

\section{Protocol: linkable one-of-many commitment}
We wish to build a linkable ring signature construction, where a signer who knows the opening of a commitment may sign messages using an anonymity set containing other commitments for which the signer does not know openings.
Included with the proof of knowledge, the signer also provides a linking tag that is the image of the signing commitment's opening under a verifiable pseudorandom function, using the method of \cite{dodis} that has previously appeared in \cite{omniring,rct3}.
Part of the soundness of the proving system relies on the proper construction of this linking tag.
Upon receipt, a verifier can check whether the linking tag has previously appeared in any other valid proof; if it has not, injectivity assures the verifier that no other signature has been produced by the (unknown) signer.

More specifically, we modify the construction of Bootle \cite{bootle}, which itself is a generalization of a construction by Groth \cite{groth}.
We produce a sigma protocol for the following relation:
$$\mathcal{R}_{\text{link}} = \left\{ \{M_i\}_{i=0}^{N-1} \subset \G, J \in \G ; (l \in \mathbb{Z},r \in \F) : M_l = rG \text{ and } U = rJ \right\}$$
Figures \ref{fig:link} and \ref{fig:link_2} describe the protocol.

\begin{figure}[htbp]
\centering
\fbox{\begin{minipage}{0.95\textwidth}
$\underline{\mathcal{P}_{\text{link}}(\{M_i\},J;(l,r)):}$
\begin{itemize}
\item Select random $r_A \in \F$ and $\left\{a_{j,i}\right\}_{i=1,j=0}^{n-1,m-1} \subset \F$.
Define $A \equiv \com(a,r_A)$.
\item Define $\left\{\sigma_{j,i}\right\}_{i,j=0}^{n-1,j-1} \subset \F$ such that $\sigma_{j,i} \equiv \delta\left(l_j,i\right)$ (using our decomposition notation), and choose random $r_B \in \F$.
Define $B \equiv \com(\sigma,r_B)$.
\item Select random $r_C \in \F$, and define $C \equiv \com(a(1-2\sigma), r_C)$.
\item Select random $r_D \in \F$, and define $D \equiv \com(-a^2, r_D)$.
\item Define coefficients $\left\{p_{k,j}\right\}_{k,j=0}^{N-1,m-1}$ such that $$p_k(x) \equiv \prod_{j=0}^{m-1} \left( \sigma_{j,k}x + a_{j,k} \right) = \delta\left(l,k\right)x^m + \sumj p_{k,j}x^j$$ for all $k \in [0,N)$ (using our decomposition notation).
\item Select random $\left\{\rho_j\right\}_{j=0}^{m-1} \subset \F$.
\item Define $\{X_j\}_{j=0}^{m-1} \subset \G$ such that: $$X_j \equiv \sumk p_{k,j}M_k + \rho_jG$$
\item Define $\{Y_j\}_{j=0}^{m-1} \subset \G$ such that: $$Y_j \equiv U \sumk p_{k,j}+ \rho_jJ$$
\end{itemize}

$\underline{\mathcal{P} \to \mathcal{V}:}$ \\
$A,B,C,D,\{X_j\},\{Y_j\}$ \\

$\underline{\mathcal{V} \to \mathcal{P}:}$ \\
$\xi \in \{0,1\}^*$ \\

$\underline{\mathcal{P}(\xi):}$
\begin{itemize}
\item Define $\left\{f_{j,i}\right\}_{i=1,j}^{n-1,m-1}$ such that $f_{j,i} \equiv \sigma_{j,i}\xi + a_{j,i}$.
\item Define $z_A \equiv r_A + \xi r_B$ and $z_C \equiv \xi r_C + r_D$.
\item Define $z \equiv r \xi^m - \sumj \rho_j \xi^j$.
\end{itemize}

$\underline{\mathcal{P} \to \mathcal{V}:}$ \\
$\{f_{j,i}\}_{j=0,i=1}^{m-1,n-1},z_A,z_C,z$
\end{minipage}}
\caption{Sigma protocol for $\mathcal{R}_{\text{link}}$}
\label{fig:link}
\end{figure}

\begin{figure}[htbp]
\centering
\fbox{\begin{minipage}{0.95\textwidth}
$\underline{\mathcal{V}_{\text{link}}(\{M_i\},J):}$
\begin{itemize}
\item For $0 \leq j < m$, let $f_{j,0} \equiv \xi - \sum_{i=1}^{n-1} f_{j,i}$.
\item Accept if and only if:
\begin{eqnarray}
A + \xi B &=& \com(f,z_A) \label{eqn:ab} \\
\xi C + D &=& \com(f(\xi-f),z_C) \label{eqn:cd} \\
\sumk M_k \left( \prod_{j=0}^{m-1} f_{j,k_j} \right) - \sumj \xi^jX_j - zG &=& 0 \label{eqn:x} \\
U \sumk \left( \prod_{j=0}^{m-1} f_{j,k_j} \right) - \sumj \xi^jY_j - zJ &=& 0 \label{eqn:y}
\end{eqnarray}
\end{itemize}
\end{minipage}}
\caption{Sigma protocol for $\mathcal{R}_{\text{link}}$ (continued)}
\label{fig:link_2}
\end{figure}

Observe that this protocol can be made non-interactive using the Fiat-Shamir heuristic, where the verifier challenge is produced using a collision-resistant hash function (modeling a random oracle) and the proof transcript \cite{fiatshamir}.

We will show that the sigma protocol is complete, sound, and zero-knowledge, the precise definitions of which are common and found in \cite{groth}.
Informally, we require the protocol be:
\begin{itemize}
\item \textit{Perfectly complete}: Given knowledge of a witness to a statement in the proof relation, an honest prover can always convince an honest verifier of the validity of the witness.
\item \textit{Special sound}: Given a statement in the proof relation, if a prover can answer multiple verifier challenges correctly, then it is possible to extract a witness for this statement.
\item \textit{Special honest-verifier zero knowledge}: Given any statement and verifier challenge, it is possible to simulate a transcript that is accepted by an honest verifier without knowledge of a corresponding witness.
\end{itemize}

\begin{theorem}
The protocol in Figures \ref{fig:link} and \ref{fig:link_2} is perfectly complete, special honest-verifier zero knowledge, and $(m+1)$-special sound.
\end{theorem}

\begin{proof}
The proof follows similarly to that of \cite{bootle}.

% Completeness
We first show perfect completeness.
Suppose the verifier receives a proof generated by an honest prover.
Equation \ref{eqn:ab} holds using the identity $$\sumi \sigma_{j,i} = 1$$ for all $0 \leq j < m$.
Equation \ref{eqn:cd} follows similarly, using the identity $$\left(\sigma_{j,i}\right)^2 = \sigma_{j,i}$$ for all $0 \leq j < m$.
To show Equation \ref{eqn:x} holds:
\begin{eqnarray*}
&& \sumk M_k \left( \prod_{j=0}^{m-1} f_{j,k_j} \right) - \sumj \xi^jX_j - zG \\
&=& \sumk M_k p_k(\xi) - \sumj \xi^j \left( \sumk p_{k,j}M_k + \rho_jG \right) - zG \\
&=& \sumk M_k \left( p_k(\xi) - \sumj \xi^j p_{k,j} \right) - \sumj \xi^j \rho_jG - zG \\
&=& \sumk M_k \xi^m \delta(l,k) - \sumj \xi^j \rho_jG - \left( r\xi^m - \sumj \rho_j\xi^j \right)G \\
&=& \xi^mrG - \sumj \xi^j \rho_jG - \xi^mrG + \sumj \xi^j \rho_jG \\
&=& 0
\end{eqnarray*}
Equation \ref{eqn:y} follows similarly:
\begin{eqnarray*}
&& U \sumk \left( \prod_{j=0}^{m-1} f_{j,k_j} \right) - \sumj \xi^jY_j - zJ \\
&=& U \sumk p_k(\xi) - \sumj \xi^j \left( U \sumk p_{k,j} + \rho_jJ \right) - zJ \\
&=& U \sumk \left( p_k(\xi) - \sumj \xi^j p_{k,j} \right) - \sumj \xi^j \rho_jJ - zJ \\
&=& U \sumk \xi^m \delta(l,k) - \sumj \xi^j \rho_jJ - \left( r\xi^m - \sumj \rho_j\xi^j \right)J \\
&=& \xi^mU - \sumj \xi^j \rho_jG - \xi^mrJ + \sumj \xi^j \rho_jG \\
&=& 0
\end{eqnarray*}
since $J = r^{-1}U$ in a valid proof.
Hence the protocol is perfectly complete.

% SHVZK
We next show that the protocol is special honest-verifier zero knowledge.
To do so, we construct a simulator that, given a random verifier challenge $\xi$, can construct a proof transcript with identical distribution to a valid proof.

First, observe that the simulator presented in the proof of Lemma 1 in \cite{bootle} translates identically to our setting.
If the simulator chooses $B \in \G$ uniformly at random, the cited lemma assures us a valid simulation of the proof elements $A,C,D,z_A,z_C,\{f^{(u)}_{j,i \neq 0}\}$; we may compute each $f^{(u)}_{j,0}$ from this.
Further, in a valid proof, $B$ is independent and uniformly distributed as well.

The proof elements $\{X_j\}_{j=1}^{m-1}$ and $\{Y_j\}_{j=1}^{m-1}$ are independent and uniformly distributed in a valid proof since the set $\{\rho_j\}$ is random and the discrete logarithm problem in $\G$ is hard, so the simulator may choose these uniformly at random.
The verification checks require that $X_0$ and $Y_0$ be uniquely determined by the other elements in the corresponding sets in both real proofs and by the simulator.

Finally, $z$ is uniformly distributed in valid proofs given random $\xi$, so the simulator may choose it uniformly at random.
Hence the construction is special honest verifier zero-knowledge.

>>>>

\documentclass{llncs}
\pagestyle{headings}

\usepackage{enumerate}
\usepackage{amsmath,amssymb}

\title{Concise Linkable Ring Signatures and Forgery Against Adversarial Keys}
\institute{Monero Research Lab, \email{\{surae,sarang\}@getmonero.org} \and Independent researcher, \email{randomrun@protonmail.com}}
\author{Brandon Goodell\inst{1} \and Sarang Noether\inst{1} \and Arthur Blue\inst{2}}

\begin{document}
\maketitle

\begin{abstract}
We demonstrate that a version of non-slanderability is a natural definition of unforgeability for linkable ring signatures. We present a linkable ring signature construction with concise signatures and multi-dimensional keys that is linkably anonymous if a variation of the decisional Diffie-Hellman problem with random oracles is hard, linkable if key aggregation is a one-way function, and non-slanderable if a one-more variation of the discrete logarithm problem is hard. We remark on some applications in signer-ambiguous confidential transaction models without trusted setup.
\end{abstract}

\section{Introduction}

First introduced in \cite{rivest} in the RSA setting and in \cite{liu2004linkable} in the discrete logarithm setting, ring signatures permit message signing on behalf of a set of public keys rather than a single public key. Ring signatures see myriad applications ranging from lightweight anonymous authentication in \cite{yang2015lightweight} to transaction protocols like Monero in \cite{noether2016ring} and CryptoNote in \cite{van2013cryptonote}. A verifier is assured that the signer knows the private key of at least one of these public keys, which are called ring members. Ring signatures are anonymous or signer-ambiguous in the sense that the verifier does not learn information from the signature about which key is the signer. We stress that methods of practical analysis such as those of  \cite{moser2018empirical,quesnelle2017linkability} can exploit metadata in real-life applications of anonymous authentication protocols to reduce anonymity.

Group signature constructions preceding \cite{rivest,liu2004linkable} require some degree of interactivity, a fixed set of participants, a trusted group manager or other trusted setup, or hardness assumptions not based on the discrete logarithm problem. Since \cite{rivest}, ring signatures have enjoyed many improvements, extensions, and modifications. For example, ring signatures are constructed in the bilinear pairing setting in \cite{zhang2002id}, key structures are generalized in \cite{abe20021}, security definitions are improved in \cite{bender2006ring}, signature size is improved in \cite{fujisaki2011sub,gu2018constant}, and traceability is introduced in \cite{fujisaki2007traceable}.

Linkable ring signature (LRS) constructions were first introduced in \cite{liu2004linkable}; in the context of transaction protocols, linkable ring signatures are the basis for anonymous transaction authentication. Linkable ring signatures guarantee that two signatures with the same ring on arbitrary messages can be publicly linked if signed using the same key. An implementation is presented in \cite{liu2004linkable} in the discrete logarithm setting; that implementation functions for similar reasons as Schnorr signatures in \cite{schnorr1991efficient}.

The signature linking tags in \cite{liu2004linkable} are unsuitable for applications where signatures must be linked key-by-key, not ring-by-ring (such as for ``double-signing'' protection in a setting where users generate new keys over time and select \textit{ad hoc} ring members). Resistance to double-signing attempts is ensured using linking tags as described in \cite{van2013cryptonote} (therein called key images). More recent work of \cite{noether2016ring} extends the approach of \cite{liu2004linkable} to enable an anonymous confidential transaction model with \textit{ad hoc} ring member selection. In \cite{noether2016ring}, transaction amounts are replaced with Pedersen commitments to amounts together with range proofs. Signatures are constructed from key vectors including differences of amount commitments as one of the keys. However, the proofs in \cite{noether2016ring} are informal and not based on rigorous security models.

Alternatives to ring signatures like more general zero-knowledge proving systems typically require a trusted party to honestly perform a setup process (as in \cite{groth,ben2014succinct,groth2018updatable}) or lack practical efficiency for large circuits (as in \cite{bulletproofs}), meaning that such systems may not be appropriate for distributed ledger applications. However, more recent approaches such as \cite{hoffmann2019efficient} show both improvements to the trust requirement as well as improvements in efficiency.

Definitions of existential unforgeability for ring signature schemes from \cite{bender2006ring} are generally inappropriate for LRS. These definitions ensure that forgeries appear to be computed from uncorrupted challenge keys by restricting choices of anonymity set members and oracle queries. We can do better with linkability.

The idea of existential unforgeability in usual digital signatures is to task an algorithm to produce any valid, non-oracle signature on any message such that the signature appears to be signed by an uncorrupted challenge key. The clear analogue for LRS schemes is to task an algorithm to produce any valid, non-oracle signature on any message such that the signature links to a challenge signature computed from an uncorrupted challenge key.  Contrast this intuition with the definition of unforgeability for usual ring signatures with respect to insider corruption from \cite{bender2006ring}, which does not count a valid signature $\sigma$ with an anonymity set $Q$ as a forgery if any key in $Q$ is corrupt or not a challenge key, or a signing oracle has been queried with the same anonymity set $Q$ and message. This leads to two problems.

The first problem is due to the disqualification of a purported forgery if there are any adversarially-selected keys or corrupted challenge keys in the anonymity set. Such a signature that links with an uncorrupted challenge key does not count as a forgery. In ring signature schemes without linkability, this restriction seems requisite to ensure that the signature appears to be signed by an uncorrupted challenge key. In applications like signer-ambiguous transaction protocols that use anonymity sets selected \textit{ad hoc}, anonymity set members should be assumed to be adversarially generated. Definitions of unforgeability should take this into account.

The second problem is due to the signing oracle restriction in this definition. An adversary could generate a valid, non-oracle signature re-using the same message and anonymity set as some challenge signature generated by the oracle. A verifier who has found more than one valid non-oracle signature on the same message with the same anonymity set, under this definition, can only conclude that at least one anonymity set member signed at least one of the signatures. This allows a malicious Mallory-in-the-middle to collect outgoing honest signatures on some honest messages and attempt to construct clone signatures on these honest messages. A sender attempting to assert culpability over a signature could then be in danger of being unable to reconstruct a signature sent to some receiver.

These problems seem to interfere with the spirit behind existential unforgeability with insider corruption from \cite{bender2006ring}: the signature is valid, not produced by an oracle, appears to have been computed from an uncorrupted challenge key, and yet is not considered a forgery.

\subsection{Our Contribution}

We relax the notion of successful forgeries to require only linking with uncorrupted challenge keys, obtaining a notion of unforgeability for linkable ring signatures that is equivalent to the definition of non-slanderability in \cite{au2006short}.  Non-slanderability allows for adversaries who can query a signature oracle with any anonymity set, even adversarially-selected anonymity sets. This models an extremely persuasive adversary who can convince users to sign messages with adversarially-selected anonymity sets. We show that non-slanderability implies unforgeability with respect to insider corruption from \cite{bender2006ring}.

We also present a Schnorr-like linkable ring signature scheme we call $d$-CLSAG that exploits key aggregation techniques to improve signature size. We describe an application for the $d$-CLSAG scheme in ring confidential transaction protocols, allowing transactions consisting of $d-1$ distinct assets simultaneously. We prove that $d$-CLSAG is linkable assuming collision resistance in key aggregation and linkably anonymous assuming the decisional Diffie-Hellman game is hard. Recall that Schnorr-like signature schemes do not cleanly reduce to the discrete logarithm assumption (\textit{c.f.}\ \cite{paillier2005discrete}), generally are only secure up to the (relatively flimsier) one-more hardness assumptions, and proof techniques typically exploit programmable random oracles with forking lemmata, leading to weak bounds. We use the general forking lemma to prove that $d$-CLSAG is non-slanderable assuming a $\kappa$-one-more variation of the discrete logarithm game is hard.

\section{Preliminaries}

Let $\lambda$ be a security parameter and $1 \leq q, \eta, \kappa \in poly(\lambda)$. Let $\mathbb{G} = \langle G \rangle$ denote a group over a field $\mathbb{F}$ with generator $G$.  Let $\mathcal{H}^s:\left\{0,1\right\}^* \to \mathbb{F}$ and $\mathcal{H}^p:\left\{0,1\right\}^* \to \mathbb{G}$ be two independent cryptographic hash functions under the random oracle model, \textit{i.e.}\ sampled uniformly from the set of all functions $\left\{0,1\right\}^* \to \mathbb{F}$ and $\left\{0,1\right\}^* \to \mathbb{G}$, respectively.

If there exists a function $f$ that is negligible in some parameter $\lambda$, and there exists $\lambda$-dependent events $A, B$ such that $\left|\mathbb{P}\left[A\right] - \mathbb{P}\left[B\right]\right| \leq f(\lambda)$, we denote this $\mathbb{P}\left[A\right] \approx \mathbb{P}\left[B\right]$. An event $A$ such that $\mathbb{P}\left[A\right] \approx 0$ is said to be negligible in $\lambda$ (or to occur with probability at most negligible in $\lambda$). The complement of an event $A$ is denoted $\overline{A}$. For a field $\mathbb{F}$, we denote the non-zero elements $\mathbb{F}^* := \mathbb{F}\setminus \left\{0\right\}$. For a finite set $S$, we define $S^*$ by interpreting $S$ as a list of letters that generate the free monoid $S^*$. For example, $\left\{0,1\right\}^*$ consists of all finite-length bitstrings.

For a set $S$, we define $\mathcal{P}(S)$ as the power set of $S$, i.e.\ the set of all subsets of $S$.

We denote vectors with bold, i.e.\ for a sequence $x_i \in \mathbb{F}$ for $i = 0, \ldots, n-1$, we denote the tuple $(x_0, \ldots, x_{n-1})$ with $\textbf{x}$. We denote the Hadamard product between vectors with $\textbf{x} \circ \textbf{y} = (x_i y_i)_i$. We begin all indices at $0$ to avoid all ambiguity.

\section{Definitions}

\subsection{Hardness Assumptions}\label{sec:hardness}

We begin by noting that if $\left\{\mu_i\right\}_{i=0}^{d-1} \subseteq \mathbb{F}$ are selected uniformly at random, then the function $\mu: \mathbb{F}^d \to \mathbb{F}$ defined by mapping $\textbf{x} \mapsto \sum_i \mu_i x_i$ has uniformly distributed output and is collision resistant. We use this property when considering linkability and linkable anonymity.

The following game is equivalent\footnote{A usual $\kappa$-one-more discrete logarithm solver can succeed at the game in Definition \ref{def:komdl} with the same probability and some extra time by merely summing solutions. A solver of the game in Definition \ref{def:komdl} can use their discrete logarithm knowledge to solve for an otherwise uncorrupted challenge key with the same probability and some extra time.} to the usual $\kappa$-one-more discrete logarithm game under the random oracle model.

\begin{definition}[$\kappa$-One-More Linear Combination Discrete Logarithm]\label{def:komdl}

Let $\kappa \geq 1$. We say any PPT algorithm $\texttt{A}$ that can succeed at the following game in time at most $t$ and with success probability at least $\epsilon$ is a $(t, \epsilon, q)$-solver of the $\kappa$-one-more discrete logarithm of linear combinations problem in $\mathbb{G}$.
\begin{enumerate}
\item Challenger draws $\left\{sk_i\right\}_{i=0}^{q-1} \subseteq \mathbb{F}$ at random, computes $pk_i := sk_i \cdot G$, sends $S := \left\{pk_i\right\}_{i=0}^{q-1}$ to $\texttt{A}$.

\item $\texttt{A}$ is granted access to a corruption oracle $\texttt{CO}$ which takes as input a public key $pk_i \in S$ and produces as output the corresponding private key $sk_i$. Corrupted keys are recorded in a table $C$.

\item $\texttt{A}$ outputs some $w \in \mathbb{F}\setminus \left\{0\right\}$, a sequence of field elements $\left\{h_j\right\}_{j=0}^{\kappa} \subseteq \mathbb{F} \setminus \left\{0\right\}$, and a subset of challenge keys $\left\{pk^*_j\right\}_{j=0}^{\kappa} \subseteq \left\{pk_i\right\}_{i=0}^{q-1}$, succeeding if and only if $w \cdot G = \sum_{j=0}^{\kappa} h_j \cdot pk^*_j$ and
 $\texttt{A}$ queried $\texttt{CO}$ no more than $\kappa$ times.

\end{enumerate}
We say that the discrete logarithms of linear combinations are computationally hard to compute in $\mathbb{G}$ if any $(t, \epsilon, q)$-solver of this game has an advantage  that is $\epsilon$ negligible in $q$.
\end{definition}

For an algorithm $\texttt{A}$ that takes as input a random tape $\rho$, a sequence of random oracle queries $\textbf{h}$ and some input $inp$ and produces $(out, idx) \leftarrow \texttt{A}(\rho, \textbf{h}, inp)$ as output, the general forking algorithm works as follows.

\begin{enumerate}[(1)]
\item  Pick a random tape $\rho$ for $\texttt{A}$ and two sequences of random oracle queries $\textbf{h} = \left\{h_0, h_1, \ldots\right\}$ and $\textbf{h}^\prime = \left\{h_0^\prime, h_1^\prime, \ldots\right\}$.

\item Execute $(out, idx) \leftarrow \texttt{A}(\rho, \textbf{h}, inp)$.

\item Set $j := idx$ and glue the oracle queries $\textbf{h}$, $\textbf{h}^\prime$ together \[\textbf{h}^* = \left\{h_0, h_1, \ldots, h_{idx - 1}, h_{idx}^\prime, h_{idx+1}^\prime, \ldots, \right\}.\]

\item Execute $(out^*, idx^*) \leftarrow \texttt{A}(\rho, \textbf{h}^*, inp)$.

\item If $idx \neq idx^*$ or $h_{idx} = h_{idx}^\prime$, output $\bot$ and terminate. Otherwise, output $(out, out^\prime, idx)$.
\end{enumerate}

This algorithm is precisely the algorithm $\mathcal{F}^{\texttt{A}}$ in the following lemma.

\begin{lemma}[General Forking Lemma]\label{lem:fork}
Let $1 \leq \eta \in \text{poly}(\lambda)$. Let $\texttt{A}$ be any PPT algorithm which takes as input some tuple $x_\texttt{A} = (x, \textbf{h})$ where we let $\textbf{h} = (h_0, h_1, \ldots, h_{q-1})$ be a sequence of oracle query responses ($\eta$-bit strings) and returns as output $y_{\texttt{A}}$ either a distinguished failure symbol $\bot$ or a pair $(\textit{idx}, y)$ where $\text{idx} \in [q]^2$ and $y$ is some output. Let $\epsilon_{\texttt{A}}$ denote the probability that $\texttt{A}$ does not output $\bot_{\texttt{A}}$ (where this probability is taken over all random coins of $\texttt{A}$, the distribution of $x$, and all choices $\textbf{h}$). Let $\mathcal{F} = \mathcal{F}^{\texttt{A}}$ be a forking algorithm for $\texttt{A}$. The accepting probability of $\mathcal{F}$ satisfies $\epsilon_{\mathcal{F}} \geq \epsilon_{\texttt{A}} \left(\frac{\epsilon_{\texttt{A}}}{q} - \frac{1}{2^\eta}\right)$.
\end{lemma}

We assume that the following game, under the random oracle model, is as hard as the usual (fixed-base) decisional Diffie-Hellman game.

\begin{definition}[Random Oracle Decisional Diffie-Hellman]\label{def:rom-ddh}

We say any PPT algorithm $\texttt{A}$ that can succeed at the following game in time at most $t$ and with success probability at least $\epsilon$ is a $(t, \epsilon, q)$-solver of the random oracle decisional Diffie-Hellman game.
\begin{enumerate}
\item Challenger draws $\left\{sk_i\right\}_{i=0}^{q-1} \subseteq \mathbb{F}$ at random, computes $pk_i := sk_i \cdot G$, computes group elements $\mathfrak{T}^{(1)}_i := sk_i \cdot \mathcal{H}^p(pk_i)$, samples random group elements $\left\{\mathfrak{T}^{(0)}_i\right\}_{i=0}^{q-1} \subseteq \mathbb{G}$, computes $S^{(j)} := \left\{(pk_i, \mathfrak{T}^{(j)}_i)\right\}_{i=0}^{q-1}$ for $j \in \{0,1\}$, samples a random bit $b$, sends $S^{(b)}$ to $\texttt{A}$, and lastly grants $\mathcal{H}^p$ access to $\texttt{A}$.

\item $\texttt{A}$ outputs a bit $b^\prime$, succeeding if and only if $b = b^\prime$.
\end{enumerate}

We say random oracle Diffie-Hellman points are hard to computationally distinguish from random in $\mathbb{G}$ if any $(t, \epsilon, q)$-solver of the random oracle decisional Diffie-Hellman game has an advantage $\left|\epsilon - 1/2\right|$ that is negligible in $q$, where this probability is measured over all functions $\mathcal{H}^p$.
\end{definition}

\subsection{Linkable Ring Signatures}

\begin{definition}\label{def:lrs} A linkable ring signature (LRS) scheme $\Pi_{LRS}$ is a tuple of algorithms $(\texttt{SETUP}, \texttt{KEYGEN}, \texttt{SIGN}, \texttt{VERIFY}, \texttt{LINK})$ satisfying the following constraints.
\begin{itemize}
\item $\texttt{SETUP}$ takes as input a security parameter $\lambda$ and produces as output some public setup parameters $\rho$.

\item $\texttt{KEYGEN}$ takes as input $(\lambda, \rho)$ and outputs a private-public keypair $(sk, pk)$.

\item $\texttt{SIGN}$ takes as input $(\lambda, \rho)$ and a triple $(m, Q, sk)$ and outputs a signature $\sigma$ or a failure symbol $\bot$. Here $m$ is a message, $Q$ is an anonymity set of public keys $Q = \left\{pk_0, pk_1, ..., pk_{n-1}\right\}$, and $sk$ is a private key.

\item $\texttt{VERIFY}$ takes as input $(\lambda, \rho)$ and a triple $(m, Q, \sigma)$ and outputs a bit $b$. Here $m$ is a message, $Q$ is an anonymity set of public keys $Q = \left\{pk_0, pk_1, ..., pk_{n-1}\right\}$, and $\sigma$ is a signature.
